Artificial Ecosystem Selection: Methane Oxidation

### 2020-07-15 R/process.Rmd
add deviance plot and model

fit <- lm(estimate ~ treat * passage, data = fluxes)
summary(fit)
selection_table <- tidy(anova(fit))

@@

fluxes %>% 
  ggplot(mapping = aes(x = passage, y = estimate, color = treat)) +
  geom_jitter(width = 0.2) +
  geom_smooth(method = 'lm') +
  labs(x = "Passage Number", y = "Methane Oxidation Rate (-k)") +
  scale_color_discrete(name = "Selection Treatment", labels = c('Neutral', 'Positive')) +
  theme_bw()

@@

log_fluxes <- fluxes
log_fluxes$estimate[log_fluxes$estimate < 0] <- 0.01

fit <- lm(estimate ~ treat * passage, data = log_fluxes)

@@

@@

@@

@@

```{r}
fluxes <- 
fluxes %>% 
  group_by(passage) %>% 
  mutate(passage_mean = mean(estimate)) %>% 
  mutate(deviance = estimate - passage_mean)

ggplot(fluxes, aes(x = passage, y = deviance, color = treat)) + 
  geom_point() +
  stat_smooth(method = 'lm')

fit <- lm(deviance ~ treat * passage, data = fluxes)
summary(fit)
```

>>>>

fit <- lm(estimate ~ treat * passage, data = fluxes)
summary(fit)
plot(fit$residuals ~ fluxes$estimate)
selection_table <- tidy(anova(fit))

@@

fluxes %>% 
  ggplot(mapping = aes(x = passage, y = estimate, color = treat)) +
  geom_jitter(width = 0.2) +
  #geom_smooth(method = 'lm') +
  labs(x = "Passage Number", y = "Methane Oxidation Rate (-k)") +
  scale_color_discrete(name = "Selection Treatment", labels = c('Neutral', 'Positive')) +
  theme_bw() + 
  geom_boxplot(aes(x = passage, y = estimate, color = treat, group = interaction(treat, passage)))

@@

log_fluxes <- fluxes
#log_fluxes$estimate[log_fluxes$estimate < 0] <- 0.01
log_fluxes$estimate <- log10(log_fluxes$estimate + abs(min(log_fluxes$estimate)) + 0.01)

fit <- lm(estimate ~ treat * passage, data = log_fluxes)
summary(fit)
plot(fit$residuals ~ log_fluxes$estimate)

@@

#ggsave('selection.pdf', width = 6, height = 4)

log_fluxes %>% 
  ggplot(mapping = aes(x = passage, y = estimate, color = treat)) +
  geom_jitter(width = 0.2) +
  #geom_smooth(method = 'lm') +
  labs(x = "Passage Number", y = "Methane Oxidation Rate (-k)") +
  scale_color_discrete(name = "Selection Treatment", labels = c('Neutral', 'Positive')) +
  theme_bw() + 
  geom_boxplot(aes(x = passage, y = estimate, color = treat, group = interaction(treat, passage)))
```

@@

plot(fit$residuals ~ fluxes$estimate_rank)

@@

gm_mean = function(x, na.rm=TRUE){
  exp(sum(log(x[x > 0]), na.rm=na.rm) / length(x))
}

ggplot(fluxes, aes(x = estimate)) + 
  facet_wrap(~ passage + treat) +
  geom_dotplot(method = 'histodot') +
  geom_vline(aes(xintercept = mean(estimate)), color = 'blue') +
  geom_vline(aes(xintercept = median(estimate)), color = 'red') +
    geom_vline(aes(xintercept = gm_mean(estimate)), color = 'green')

@@

```{r}
deviance_se <- 
  fluxes %>% 
  select(treat, passage, estimate) %>% 
  group_by(passage, treat) %>% 
  summarize(se = se(estimate)) %>% 
  pivot_wider(names_from = treat, values_from = se) %>% 
  mutate(deviance_se = p + n) %>% 
  pull(deviance_se)

deviance <-
fluxes %>% 
  select(treat, passage, estimate) %>% 
  group_by(passage, treat) %>% 
  summarize(mean = median(estimate)) %>% 
  pivot_wider(names_from = treat, values_from = mean) %>% 
  mutate(deviance = p - n)

deviance$se <- deviance_se

fit <- lm(deviance ~ passage, data = deviance)
summary(fit)

fit <- rma(deviance~passage,se^2,method="FE",data = deviance)
fit

summary(fit)
plot(fit)

ggplot(deviance, aes(x = passage, y = deviance, ymin = deviance - se, ymax = deviance + se)) + 
  geom_pointrange() + 
  geom_abline(intercept = fit$beta[1], slope = fit$beta[2], color = 'blue')
